%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research intern} % Job title
    {RobotLab [under supervision of Prof. Qixin Cao]} % Organization
    {SJTU} % Location
    {Oct. 2019 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Haili Wang on path planning for multi-robot scene. Have a co-authored article.}
        \item {Now working on a project regarding the smart-rehabilitation-system. Fields related are human pose estimation and human action evaluation. Using some recommendation algorithms learned from school.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Research intern} % Job title
    {Future Network Innovation Laboratory [under supervision of Prof. Yang Xu]} % Organization
    {FDU} % Location
    {Apr. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched into ways to model cache replacement algorithms to speed up simulations, to recognize request patterns and to find ways (mainly cache pollution attacks) to disrupt the locality of CDNs and corresponding countermeasures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend engineer intern} % Job title
    {ChenXi Studio} % Organization
    {Shanghai} % Location
    {June. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped with the development of a project website that involves generating and returning user-information-related-pictures, had 600+ users.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research intern} % Job title
    {System Security Lab [under supervision of Prof. Yuan Zhang]} % Organization
    {FDU} % Location
    {Sep. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched into the topic of Javascript RFCs through vulnerable WebView component in android systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
