%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{School Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Programming A}
    {the game of the arena chess}
    {FDU}
    {2016.12}
    {
      \begin{cvitems} % Description(s)
      \item {100\% completion, the realization of the JavaFX-based GUI, the corresponding user mouse and keyboard operation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Object-Oriented Design}
    {2048 games}
    {FDU}
    {2017.12}
    {
      \begin{cvitems} % Description(s)
      \item {A C++ QT-based GUI2048 game, using depth search to achieve AI functionality.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Introduction to Web Applications}
    {Image sharing website}
    {FDU}
    {2017.06}
    {
      \begin{cvitems} % Description(s)
      \item {A web interface. PHP + MySQL as backend, frontend HTML, CSS, JavaScript, user authentication with cookies, encryption using hashing with salt.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Structure and Algorithm Design}
    {Chess AI}
    {FDU}
    {2017.12}
    {
      \begin{cvitems} % Description(s)
      \item {min-max search, alpha-beta pruning, search layer: 4.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer System Foundation (2)}
    {CLI multi-threaded chat room}
    {FDU}
    {2017.12}
    {
      \begin{cvitems} % Description(s)
        \item {thread pool monitoring message, specify ip+port to achieve message transmission.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering (Group Work)}
    {Calendar Notepad}
    {FDU}
    {2018.06}
    {
      \begin{cvitems} % Description(s)
        \item {This course focuses on design patterns and code refactoring. Responsible for backend development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Graphics}
    {WebGL project}
    {FDU}
    {2018.06}
    {
      \begin{cvitems} % Description(s)
        \item {Draw a scene with WebGL, user keyboard event to achieve camera perspective change and omnidirectional movement}
        \item {Realized keyboard event control object visibility, realize keyboard event control transformation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Neural Network and Deep Learning (Group Work)}
    {Chinese ancient poetry generation}
    {FDU}
    {2018.06}
    {
      \begin{cvitems} % Description(s)
        \item {Based on TensorFlow framework, using LSTM.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Distributed Systems}
    {New York Taxi Data Analysis}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Doing massive data analysis on Spark.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Data Science}
    {Turkish population data analysis}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Doing massive data analysis on Spark. Machine learning algorithms applied.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Artificial Intelligence (Group Work)}
    {Gomoku on piskvorkGomoku agent implemented with MCTS}
    {FDU}
    {2019.06
    2019.06}
    {
      \begin{cvitems} % Description(s)
      \item {ADP; Threat-space search applied.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Social Network Mining (Group Work)}
    {Movie recommendation algorithms for users}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Using web crawlers to gather data (from Douban) and multiple recommendation algorithms to make reasonable choices of recommendation to users.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Statistical machine learning (Group Work)}
    {[Kaggle] Box office prediction}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Using LightGBM for prediction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Statistical machine learning (Group Work)}
    {Bilibili Data Analysis}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Using web crawlers to gather data (from Bilibili) for Data Analysis on video uploaders.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Financial Time Series in Data Mining (Group Work)}
    {Residential electricity usage data analysis}
    {FDU}
    {2019.06}
    {
      \begin{cvitems} % Description(s)
        \item {Using DTW for time series classification and LSTM for time series prediction. Data from Bureau of Shanghai Electric Power.}
        \item {Time series analysis on search engine searches for keyword "Big Data";}
        \item {Using web crawlers to gather data (from Baidu Index) to predict future market size of the "Big Data" industry.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
